% vim: ft=tex
%!TEX root=sbst2016.tex

\vspace*{-.5em}

\section{Shared Repositories}
\label{sec:repositories}

\input{figures/statistical_repositories}

It is important to underscore the fact that this paper's goal is not to call into question the ways in which the
``Hitchhiker's Guide'' has benefited the SBST community. Rather, we propose that it is time to build on the noteworthy
foundation set by Arcuri and Briand by encapsulating their theory and practical suggestions into a free and open-source
statistical software package shared through GitHub.

Figure~\ref{fig:statistical_repositories} lays out our vision for the ``free vehicles'' that will improve the
methodological maturity of the ``hitchhikers'' in the SBST community. The core of our proposal is the ``sbst-analysis''
R package that is implemented with the R ``devtools'' package and hosted on GitHub. R packages, as described and
produced by Wickham, support the disciplined creation and delivery of self-contained R source code~\cite{Wickham2015}.
This repository will provide well-documented functions implementing all of the best practices for the statistical
analysis of the randomized algorithms used by SBST researchers.

Since this repository is publicly available, inquisitive researchers can easily clone it (as indicated by the
\codecopygit~annotation in Figure~\ref{fig:statistical_repositories}) and then study the functions to better understand
their operation and assumption(s). When new analysis ideas emerge (e.g., the transformations proposed by
Neumann~\etal~\cite{Neumann2015}), then the developers of these new methods can fork sbst-analysis (as shown by the
\codeforkgit~label), add new functions or modify the existing ones, and then submit a merge request back to the
maintainers of sbst-analysis; once approved the new code will be available to the community, thereby speeding the uptake
of this new analysis idea.

Now, let's assume that sbst-analysis exists and Tom decides to use it to help him calculate effect sizes. Tom follows
the easy-to-understand recommendations by Wickham and creates his own Git repository for an R package called
``atdg-analysis'' that installs sbst-analysis as its main provider of functionality and contains all of the needed code
and data, as shown by the \codedatagit~label. Since sbst-analysis uses R's dplyr package to efficiently manipulate large
data sets, the code in Tom's package correctly completes the advocated data transformations.  Tom can now see that the
un-transformed data leads to an effect size supporting the opposite conclusion of the \atwelve~that was computed with
the transformed data.

Moreover, Elaine might leverage the thorough documentation in sbst-analysis to discover that {\tt wilcox.test} is a
correct analysis function for her ordinal data. At this point, both Elaine and Tom can use a standard like RMarkdown to
write a report that calls the functions from their R packages and, additionally (as indicated by the
\codeeditgit~label), includes written content explaining the assumptions and analysing the results. These reports would
allow both Elaine and Tom to best follow the advice of Arcuri and Briand to ``provide full statistics for the collected
data''~\cite{Arcuri2014}. When these reports are input into the RMarkdown compiler, the results of running the
embedded R code (e.g., graphs, summarized data tables, and statistical output) are available to Elaine and Tom when they
want to submit their next paper to an SBST-related venue.

It is worth noting that Figure~\ref{fig:statistical_repositories} uses the \faGit~symbol to suggest that Tom and Elaine
will store all of their deliverables in a Git repository, which is either private or publicly hosted by GitHub. Even though
the proposed approach only requires the sbst-analysis package to be publicly available on GitHub, the SBST community will further
benefit if the researchers using it agree to also make their analysis packages, reports, results, and papers accessible
to others.
